Metadata control document

### 2023-06-21 metadata/metadata_control.Rmd
Switched isotopes to correct option

```{r}
clean_stans <- "https://raw.githubusercontent.com/IngallsLabUW/" %>%
  paste0("Ingalls_Standards/master/Ingalls_Lab_Standards.csv") %>%
  read_csv() %>%
  filter(Column=="HILIC") %>%
  mutate(polarity=case_when(
    z==1 ~ "pos",
    z==-1 ~ "neg",
    TRUE~"unknown"
  )) %>%
  select(compound_name=Compound_Name, compound_type=Compound_Type, 
         formula=Empirical_Formula, stan_mz=mz, stan_rt=RT_minute, 
         mix=HILIC_Mix, conc_um=Concentration_uM, date_added=Date_Added, 
         name_old=Compound_Name_Original, kegg_id=KEGG_Code, polarity,
         peak_quality=Peak_Quality) %>%
  mutate(compound_name=case_when(
    compound_name=="Ethyl aminobenzoate"~"Ethyl aminobenzoate?",
    TRUE~compound_name
  ))
extra_stans <- "https://raw.githubusercontent.com/IngallsLabUW/" %>%
  paste0("Ingalls_Standards/master/data_extra/custom_stans.csv") %>%
  read_csv()

>>>>

```{r}
clean_stans <- "https://raw.githubusercontent.com/IngallsLabUW/" %>%
  paste0("Ingalls_Standards/8fb6679505f692ec7d1cb4bf54ff1c5d4967c9a6/") %>%
  paste0("Ingalls_Lab_Standards.csv") %>%
  read_csv() %>%
  filter(Column=="HILIC") %>%
  mutate(polarity=case_when(
    z==1 ~ "pos",
    z==-1 ~ "neg",
    TRUE~"unknown"
  )) %>%
  select(compound_name=Compound_Name, compound_type=Compound_Type, 
         formula=Empirical_Formula, stan_mz=mz, stan_rt=RT_minute, 
         mix=HILIC_Mix, conc_um=Concentration_uM, date_added=Date_Added, 
         name_old=Compound_Name_Original, kegg_id=KEGG_Code, polarity,
         peak_quality=Peak_Quality) %>%
  mutate(compound_name=case_when(
    compound_name=="Ethyl aminobenzoate"~"Ethyl aminobenzoate?",
    TRUE~compound_name
  ))
extra_stans <- "https://raw.githubusercontent.com/IngallsLabUW/" %>%
  paste0("Ingalls_Standards/master/data_extra/custom_stans.csv") %>%
  read_csv()
